\documentclass[10pt, letterpaper]{article}
\usepackage[utf8]{inputenc}
\usepackage[margin=3cm]{geometry}
\usepackage{titling}
\setlength{\droptitle}{-9em}

\usepackage{enumitem}
\setlist{noitemsep}


\begin{document}

\title{Maia Kapur, MSc}
\author{maia.kapur@noaa.gov}

\maketitle
\vspace{-15mm}
\noindent\makebox[\linewidth]{\rule{\paperwidth}{0pt}}
\section*{Education}
\begin{tabular}{lll}

MSc & University of Hawaii, Marine Biology & 2016 \\
BSc & University of California Berkeley, Environmental Science & 2014 \\
\end{tabular}

\section*{Employment History}
\textbf{Fisheries Research \& Monitoring Division, Pacific Islands Fisheries Science Center, National Oceanic \& Atmospheric Administration}, \textit{Fisheries Assessment Specialist} (Feb 2017-current)
\begin{itemize}
\vspace{-2.5mm}
  \item Stock assessment specialist.
  \item Data analyst.
\end{itemize}
\textbf{Fisheries Research \& Monitoring Division, Pacific Islands Fisheries Science Center, National Oceanic \& Atmospheric Administration}, \textit{Fisheries Biosampling Associate} (May 2016-Feb 2017)
\begin{itemize}
\vspace{-2.5mm}
\item Oracle database developer \& manager.
\item Statistical modeler.
\end{itemize}
\textbf{Environmental Protection Agency, USA}, \textit{Research Assistant}, (Dec 2015- May 2016)
\begin{itemize}
\vspace{-2.5mm}
\item Graduate resesarch scientist
\item Spatial watershed-to-reef conservation prioritization model, statistical summaries of fish surveys.
\end{itemize}
\textbf{Hawaii Conservation Alliance, HI}, \textit{Geospatial Data Librarian}, (Nov 2015- Aug 2016)
\begin{itemize}
\vspace{-2.5mm}
\item ArcGIS Online database manager.
\item Compliance adherence \& metadata compilation for terrestrial and marine conservation web GIS.
\end{itemize}
\textbf{United States Geological Society, Hawaii}, \textit{Research Assistant}, (Aug 2014- Dec 2015)
\begin{itemize}
\vspace{-2.5mm}
\item Graduate resesarch scientist.
\item Development and testing of spatial reef fishery dynamics model for Main Hawaiian Islands.
\end{itemize}


\section*{Publications}
\noindent \textit{First-author:}

\hangindent=0.5cm \noindent \textbf{Kapur, M. R.}, Franklin, E.C. 2017. \textit{Simulating future climate impacts on tropical fisheries: are contemporary spatial fishery management strategies sufficient?*} Canadian Journal of Fisheries and Aquatic Sciences.  DOI: 10.1139/cjfas-2016-0200 
*This work was included in a special edition on spatial simulation modeling in fisheries. \\

\noindent \textit{Papers Submitted for Peer Review:} 

\hangindent=0.5cm \noindent Taylor, B.T., Brandl, S., \textbf{Kapur, M.R.},  Johnson, G., Robbins, W., Huveneers, C., Renaud, W., Choat, J.H. 2017.
\textit{Bottom-up processes mediated by habitat disturbance drive demographic traits of coral-reef fishes.} Ecology (in review).\newline

\noindent \textit{Stock Assessments:}

\hangindent=0.5cm \noindent Langseth, B., Syslo, J., Yau, A., Brodziak, J. \textbf{Kapur, M.R.}. \textit{Stock Assessment for the Main Hawaiian Islands Deep7 Bottomfish Complex Through 2015}. NOAA Technical Memorandum NMFS-PIFSC-XX. 2017.  \newline


\noindent \textit{Working Papers:}

\hangindent=0.5cm \noindent Winker, H., Carvalho, F., \textbf{Kapur, M.R.} Parker, D., Kerwath, S.. JABBA goes IOTC: ‘Just Another Bayesian Biomass Assessment’ for Indian Ocean Blue shark and swordfish. \textit{ Indian Ocean Tuna Commission.} IOTC-2017-WPB15-INF02. Available at: http://www.iotc.org/documents/jabba-just-another-bayesian-biomass-assessment 

\hangindent=0.5cm \noindent  \textbf{Kapur, M.R.}, Yau, A. Size Compositions and Sex Ratios of Oceanic Whitetip Sharks and Giant Manta Rays for Longline Fisheries in the Pacific Islands Region. \textit{ PIFSC Working Paper}, WP-17- 000, 23 pp.

\hangindent=0.5cm \noindent  \textbf{Kapur, M.R.},  Brodziak, J. A., Fletcher, E. J., Yau, A. J. 2017. Summary of Life History and Stock Assessment Results for Pacific Blue Marlin, Western and Central North Pacific Striped Marlin, and North Pacific Swordfish. \textit{International Scientific Committee for Tuna and Tuna-like Species in the North Pacific Ocean.} PIFSC Working Paper, WP-17-004, 50 p. doi:10.7289/V5/WP-PIFSC-17-004. Available at: http://www.pifsc.noaa.gov/library/pubs/WP-17-004.pdf

\hangindent=0.5cm \noindent  Sculley, M. S., Brodziak, J. A., Yau, A. J., \textbf{Kapur, M.R.}. An Exploratory Analysis of Trends in Swordfish (Xiphias gladius) Length Composition Data from the Hawaiian Longline Fishery. \textit{International Scientific Committee for Tuna and Tuna-like Species in the North Pacific Ocean.} PIFSC Working Paper, WP-17-002, 48 p. doi:10.7289/V5/WP-PIFSC-17-002. \\

\section*{Invited Lectures and Conference Presentations}

\noindent \textbf{School of Aquatic and Fisheries Science, University of Washington - Seattle}, \textit{Simulating Demography and Selective Harvesting Effects on Hawaiian Kona Crab}. Seattle, WA (Sep 2017)

\noindent \textbf{International Coral Reef Conference}, \textit{Testing Spatial Harvest Strategies for Hawaiian Coral Reefs: A Biophysical, Metacommunity Approach }. Honolulu, HI (June 2016).

\noindent \textbf{Graduate Climate Conference}, \textit{A Decision-Support tool for Hawaiian Reefs under Climate Change}. Woods Hole, MA (Nov 2015).

\noindent \textbf{Island Futures Conference}, \textit{Testing Spatial Harvest Strategies for Hawaiian Coral Reefs: A Biophysical, Metacommunity approach}. Honolulu, HI (August 2015).

\section*{Awards and Fellowships}
\textbf{Graduate Assistantship}, Environmental Protection Agency (2016) - \$26,250 per annum \\
\textbf{Garduate Assistantship}, United States Geological Survey (August 2014 - Dec 2016) - \$26,250 per annum \\
\textbf{Scholarship}, American Geophysical Union Early Carrer Scientist Travel Grant (February 2016) - Declined invitation because of prior engagements \\
\textbf{Scholarship}, Travel Grant, MIT-Woods Hole Graduate Climate Conference (November 2015) - \$300 \\
\textbf{Dean's List}, University of California at Berkeley (2010) \\

\section*{Computer Skills}
 R, Stan, JAGS, git, SQL, Arc, Oracle, \LaTeX, MS Office

\end{document}
